\chapter*{Start}\label{start}
\addcontentsline{toc}{chapter}{Start}

\enquote{\noindent\textsc{{How many kids would you have had?}} I mean, if it were not for\dots{}}

Her voice slowly fades out, her face shying away the same way it she does every time the topic of her mother is approached. So many times, so many years, and it still pains me to see how she gets the guilty blow-back from herself every time she does it, and yet she cannot avoid repeating it.

I say, \enquote{Hey Ladybug, don't get blue---it does not hurt like before.} It's a lie, it still hurts. And she senses it somehow.

I reach out for her, bringing her to a hug as she dramatically trudges into the living room. I sniff her hair for a while and notice: smoke. I ask, \enquote{Were you smoking?}

She takes some distance, opens her mouth demonstratively and exhales in my direction: negative for smoke. 

\enquote{It was Justyna,} she says. \enquote{We gathered in the park, she's got the confirmation of a position. She will start right after finishing training, in some months. She was musing that, with her and Thomas having confirmed positions, they can start to make plans for a baby.}

\enquote{So, \emph{this} is where this kid-number-story comes from,} I commented. \enquote{Now tell me: how will Justyna have a baby and smoke? Or\dots{}}

\enquote{\dots~she will have to stop when she decides to get pregnant, so she wants to smoke now while she can,} she complements my line of thought. She was good at doing that---like her mother. I usually hate when people try to predict what others are about to say, but only because most of time most people get it wrong. Yael doesn't. 