\chapter*{Acceptance}\label{acceptance}
\addcontentsline{toc}{chapter}{Acceptance}

I leave her busy with her thoughts, as I imagined she would be after the conversation. I tell her that I am open to proceed further, but also that I will share with her some resources to orient her in the flood of information that the internet provides. It does not help that very little public facing information is in Germany, because the procedure is not allowed here and in the European Union.

But what really annoys me is the amount of information that is misleading or outright false, mostly from ads promoting clinics in other countries. It is inevitable that she will see the bad websites, sooner or later, but I would like her to read my selection first. 

I do not share all at once; I give her at first enough reading for a part of today, so we can discuss after she finishes. As part of my curation, I share scientific and public facing articles on identity dysphoria disorders, which can vary from over-identification to consciously targeted negation of any similarity with the root. 

She reads in her tablet, still in the kitchen, and does not care to sit on the couch or lie on her bed. I stay around in case she has any questions and pretend to read something in my device, but I actually just watch her. Of course she looks a lot like her mother, even if I tried to convince me otherwise, but not like I feared she could become when she was young. The most striking similarities I notice are actually in her behavior, such as now, how deeply she can concentrate on something, and that flickering in the eyes that is the same.

It pains me to know that I will never be able to talk about that with her.

\bigskip\thinspace\noindent\textsc{After she finishes the readings I have lunch ready.} We eat it in silence and I suggest that we go for a walk in our neighborhood. I do not tell why, but it is to anchor her through the familiar sights, to avoid dissociating from the life she had until now. To reassure her that she is still the same person.

It seems to work, I would like to think. Several times she stops and looks at sights that she saw thousands of times before, and I wonder if she is seeing something new or acknowledging the old. I do not ask, I fear the answer.