\chapter*{Acquaintance}\label{acquaintance}
\addcontentsline{toc}{chapter}{Acquaintance}

He does it well. I can see that he's been preparing for this. He brings the cookies that I once liked but have for a while overgrown. He wants to make me comfortable. 

I cannot keep hating him like I was doing just until now.

He starts from the very obvious: how they met each other. It does not interest me. I do not think that people are themselves when they are meeting someone new. I am not myself when meeting someone new.

I try not to interrupt, it is obvious that he is heading toward what I whish. 

Now: her first personal wish. 

Why did she want to go there?

Because it was the city of her family. 

This does not make sense, Jews were not Germans citizens.

At some point, they had to become, Nitzy, it was enforced law.

So everything was un-enforced decades later?

Ironies of history, but, yes\dots

And what happened there?

Not much, we visited the place where her family lived, and talked about what it meant.

Silence; tears; I don't know why, I do not know what to make of that, because she---\emph{Shoresh}---had interests that I cannot understand, and that he cannot communicate.

How many more, of relatives, I mean?

Not many, there is a branch of the family, but it is not close.

Have you had contact with them?

No, never, they emigrated to the Americas.

Why not?

Hey, this was her family, I do not know everything.

Go on, tell me more.

Wait, don't you want to visit the location?

Do not distract me, we have only today for information, but forever for places. 

He seems struck. I regret saying that, it sounds like a type of goodbye.

She's chosen your name.

What?

Yes, we talked often about that, which names to choose in case\dots

So you were\dots~planning on having a child?

Yes, we even got genetically tested.

I have to think for a while.

So the whole talk about thalassemia\dots

\dots~was already known. Yes, both me, and her, had it, and so do you.

This makes me dizzy, I need to ask now.

So, it might be that even if she had not died, you would have opted to have a kid this way, as you yourself did alone?

He takes his time to answer.

\enquote{Yes.}