\chapter*{Back}\label{back}
\addcontentsline{toc}{chapter}{Back}

\emph{Frühling}\thinspace\footnote{\emph{German}: spring.} in Germany brings light to everyone. The very name sounds like it. I hear it through the window before I open my eyes.

When do I open my eyes, Father is sitting on a chair by my bed, looking at me. With a smile, Father says, good morning.

Good morning, I smile back.

How are we today?

Better than yesterday, worse than tomorrow.

I love you.

I say, I know that.

And?

Thank you.

Not that.

I love you too.

If you stop saying it, I will forget it. Do you want that?

I don't. You won't.


\thinspace\textsc{After coming back from sleep,} I still need time to catch up with the body. I can observe it backwards. It feels that something changed in how I thought. 

As I watch the ceiling, I realize, like I have been doing in the last days, how much of a toll this must have been taking on Father.

After we have breakfast, he will go to work and check on me during the day. He is lovely.

I wish I could assure him that I need less intensive monitoring and care, but I realize I am not capable of changing this. I will have to show it through the facts and results.

So I send him pictures of me:

\begin{itemize}
	\item smiling while feeding the cat of the neighbor who is away (this is
	not a lie)
	\item enjoying doing workout at home (this is a lie)
	\item random things like varied city landscapes, buildings, etc (this is not
	a lie)
	\item sunbathing and reading books in sunny parks (they are not a lie)
\end{itemize}

I will not let anyone judge me on lying: if anyone knew him as I do, they would do the same.

I do not try to play being fully okay, and he would notice if I did. But what is amiss, I still cannot see what it is. But I am sure I will; I might not do it alone---but I am not.

%\input{separators/sep-line-1.tex}
%\input{separators/sep-ast-1.tex}
%\input{separators/sep-scshape-1.tex}
\input{separators/sep-3-diamond-1.tex}
%\input{separators/sep-quadding-1.tex}
%\input{separators/sep-3-asterisk-1.tex}

I had him arrive earlier and worried, but it should be worth the trouble: I had prepared for him his favorite hummus recipe, with the marinated Aubergines he loves more than me, with garlic olives, all with \emph{Rotwein}\thinspace\footnote{\emph{German:} red wine.} of his favorite local winery and his hateful \emph{Vollkornbrot}; I am recovered enough to survive it.

For the evening, I chose a different outfit, and was gladly finishing last touches to the food when he arrived. Things from old times, when I was younger and experimented with dresses and things for fun, one of the few that I selected to save from the \enquote{old life.}

Mal entered our kitchen and froze. It took me milliseconds to notice something was wrong. Then it took me even less milliseconds to notice that what I was wearing were the same yellow cotton dress and a silver butterfly pendant that I chose for her to meet him at his second arrival at Tel-Aviv. Mal was sitting on a chair, looking at me from below with teary eyes.

I closed my eyes and clamped my ears and started crying as if ignoring things would undo them. I was falling down again---but now something was different; I felt arms around me and I could run my hands around them; I tasted tears not mine and they smelled like her. I opened my eyes and he was not visible because we were one and I can only see myself with a mirror.

Yes, on his birthday Mal chose me. Or he was just diverting attention from himself, which he always does, which ends same way.

He did not make it openly, but feel did I do. Already before this last crisis I was trying to find a way to get a trade in Germany. The official ways here expect a traceable life path, which is nowadays increasingly sensitive to scrutiny.

The way he conducted the interaction awoke something in me. He asked questions for which he knew the answers. He nodded in acknowledgment as if he was surprised. He smiled as if it meant only appreciation. It might be strange to anyone who was never there down deep that having ideas was a remarkable thing---but they are.

%\input{separators/sep-line-1.tex}
%\input{separators/sep-ast-1.tex}
%\input{separators/sep-scshape-1.tex}
\input{separators/sep-3-diamond-1.tex}
%\input{separators/sep-quadding-1.tex}
%\input{separators/sep-3-asterisk-1.tex}


\enquote{It is beautiful---wonderful,} I said.

Mal smiled pleased, said: \enquote{Glad you liked it.}

I retorted, \enquote{But it was a risky move.}

\enquote{Well worth seeing your face now.}

It was a piece of jewelry that I had never seen before---or if I had seen, unconsciously suppressed: a very realistic prosthetic eye, nearly identical to my natural one, mounted into a silver socket, sculpted eyelashes, making a pendant, on a simple silver chain with round links. I wonder how he did it---I do not remember him taking any photos of me, he knows that I do not like being photographed.

I do not know if he intuited what I then realized, but I noticed at that moment that even after all those years of practice I still had some wariness, self-consciousness about my eyes. Wearing it, looking at the mirror, felt like this was what was missing.

Oh, how lucky I am to have him.
