\chapter*{Care}\label{care}
\addcontentsline{toc}{chapter}{Care}

I did not expect it so soon. I was aware that, at some point, some crisis might erupt, but this is just the third day.

She came back from the time with her pals, greeted me in a perfunctory way, went to her room and is now lying on her bed, on her right side, looking at the emptiness of the wall in front of her. No crying, no movement. I take a look regularly, probably each half an hour, but I see no change.

Around twenty I bring her tea, the type she has preferred lately, also some nuts and dried fruits. She likes that, and it is energy food that does not require much on her side.  

When it is half past twenty-two I come into her room and sit by her side. The whole time she has not moved. 

I look at her face, which shares so much of her mother, and yet has so much of her own. I seem to see also something of mine there, but I know that it is probably an illusion, or, at best, some mannerism which she learned from me. 

Looking at her I ask of myself, was it fair? To bring her into this world in this way? Was I being so selfish as to not imagine that one day she would suffer?

I say to myself that I would die if that would spare her the suffering she is living through now, but that is a cheap saying, because it is impossible to prove it true. Worse than that, it would mean abandoning what I did.

There is only one way forward, and it is together with her. 

She seems to listen to my thoughts, she turns her face lightly to me. My face asks something. Her face expression tells me \enquote{Not yet.} 