\chapter*{Crisis}\label{crisis}
\addcontentsline{toc}{chapter}{Crisis}

I come back, lie in bed. Stay there. He comes, goes, brings me food, tea.

Next morning he comes again. I turn to him, I say, I always knew something was wrong.

It is a lie 

I always knew you were lying.

It is a lie.

I am not who I thought I am. 

It is true. He gives me no answer because it is not possible. I hear him calling my work, his work, of.

I say, no. I need this. I give up.

He comes closer, caresses the back of my neck, like aways. He whispers, this changes nothing about who you are. I love you. You, not genes or cells.

I shrink down to the smallest I could, until I fit into his hand. I slow time to the slowest I can, until all thoughts almost stop. I want to stop time for forever but I fail. I want to become so small that I vanish but I fail.

I want to fail to keep existing. But even at that want, I fail.

\bigskip\thinspace\textsc{New lights wake me up.} My eye sees a new world. New sounds come through the window. A new pair of breathe in and out. A new heartbeat gives me rhythms. 

New arms were holding me, still asleep. He is not new; I hold him closer, afraid that he can get too small and slow to love me. He cannot, he is my father. 

I am there with him until the universe ends. I see all stars shutting down. I am alone with him and that feels correct. I wish this could last forever. It does not. 

\bigskip\thinspace\textsc{He brings me food several times}. I do not refuse it but I do not see the reason. He leads me to the toilet several times but I do not see the reason. He brings me water and milk and tea. He did it several times, but I do not see the reason. I opened my eyes when he did all of that and I see it all but I see no reason. All several times happened several times, then this also several times and I see no reason.

He holds me me. I shrink down to be smaller as a human heart. I do not expect a reason.

\bigskip\thinspace\textsc{I start to move but it is no help.} I need to see where to go, but I see no light. I bump onto things, then I give up. One time I grasped something and identified it: Father. I wished that he would love me again, help me. I wished that he could see my wish. 

But his eye is not like mine. I wish he had my eye but I regret wishing this because my eye is not really mine and I do not want him to feel what this is. 

\bigskip\thinspace\textsc{A sound that matches the rhythms of my heart.} I see, smell it. I try to grab it and fail. I try some more and fail. I am trying the wrong way: I try with my hands, then I find it. I open it up and it told me something: Nitzy. 

Nitzy, dear, what did you say?

Father, help me.

Yes, yes, stay with me.

Please, do not go away.

Yes, I am here; look here, look at me. Nitzy, I am here, never away.

Where are we?

We are home. Our home. Stay here, let me hold you.

Why are you here?

Because I love you, remember this. Keep this.

I do not want to go away.

You never will, Nitzy. Can I show you? Let me show you.

I felt his arms around me. I have tears now. I feel other tears also. I recognized them: they smelled like Father's.


\bigskip\thinspace\textsc{I feel so weak,} like there is no body down there. He's being so being so careful as if he was carrying a baby. I feel like a baby.

I feel sorry for him. I wish I would feel worth enough to feel sorry for myself.

Feeling sorry for him means motivation: I want to honor his effort. 

I bring him close, when and if he let me do it. He caresses me, as a kind of payment. I feared caressing him, because it would not be enough.

At first I felt it not. I saw him doing, only.

I got used and then I felt them. They ended in tears, but I did not regret it. It was good tears.

At some point I forget the fear and touch him without touching. He senses even though I try to be as light as I could. He smiles.

%\input{separators/sep-line-1.tex}
%\input{separators/sep-ast-1.tex}
%\input{separators/sep-scshape-1.tex}
\input{separators/sep-3-diamond-1.tex}
%\input{separators/sep-quadding-1.tex}
%\input{separators/sep-3-asterisk-1.tex}


\emph{Frühling}\thinspace\footnote{\emph{German}: spring.} in Germany brings light to everyone: the very name sounds like it. I hear it through the window before I open my eyes.

When do I open my eyes, Mal is by my side, looking at me. He says, \enquote{Good morning.}

I smile a \enquote{Good morning.}

\enquote{How are we today?}

\enquote{Better than yesterday, worse than tomorrow.}

\enquote{I love you.}

I say, \enquote{I know that.}

\enquote{And?}

\enquote{I love you too.}

Mal points out, \enquote{If you stop saying it, I will forget it. Do you want that?}

I smile a brighter smile, \enquote{No, I don't.}

\enquote{Keep that in mind and practice it. Meanwhile, I will do breakfast. Do not try to run away; if you do, tell me before.}

\enquote{Yes, can do.}

After coming back from sleep, my thoughts still need some time to catch up with the body; I can observe it backwards. Mal also.

As I watch the ceiling, I realize, like I have been doing in the last mornings, how much of a toll this must have been taking on Mal.

After we have breakfast, he will go to work and check on me during the day. He is lovely.

I wish I could assure him that I need less intensive monitoring and care, but I realize I am not capable of changing this. I will have to show it through the facts and results.

So I send him pictures of me:

\begin{itemize}
	\item smiling while feeding the cat of the neighbor who is away (this is
	not a lie)
	\item enjoying doing workout at home (this is a lie)
	\item random things like varied city landscapes, buildings, etc (this is not
	a lie)
	\item sunbathing and reading books in sunny parks (they are not a lie)
\end{itemize}

I will not let anyone judge me on lying: if anyone knew him as I do, they would do the same.

I do not try to play being fully okay, and he would notice if I did. But what is amiss, I still cannot see what it is. But I am sure I will; I might not do it alone---but I am not.

%\input{separators/sep-line-1.tex}
%\input{separators/sep-ast-1.tex}
%\input{separators/sep-scshape-1.tex}
\input{separators/sep-3-diamond-1.tex}
%\input{separators/sep-quadding-1.tex}
%\input{separators/sep-3-asterisk-1.tex}

I had him arrive earlier and worried, but it should be worth the trouble: I had prepared for him his favorite hummus recipe, with the marinated Aubergines he loves more than me, with garlic olives, all with \emph{Rotwein}\thinspace\footnote{\emph{German:} red wine.} of his favorite local winery and his hateful \emph{Vollkornbrot}; I am recovered enough to survive it.

For the evening, I chose a different outfit, and was gladly finishing last touches to the food when he arrived. Things from old times, when I was younger and experimented with dresses and things for fun, one of the few that I selected to save from the \enquote{old life.}

Mal entered our kitchen and froze. It took me milliseconds to notice something was wrong. Then it took me even less milliseconds to notice that what I was wearing were the same yellow cotton dress and a silver butterfly pendant that I chose for her to meet him at his second arrival at Tel-Aviv. Mal was sitting on a chair, looking at me from below with teary eyes.

I closed my eyes and clamped my ears and started crying as if ignoring things would undo them. I was falling down again---but now something was different; I felt arms around me and I could run my hands around them; I tasted tears not mine and they smelled like her. I opened my eyes and he was not visible because we were one and I can only see myself with a mirror.

Yes, on his birthday Mal chose me. Or he was just diverting attention from himself, which he always does, which ends same way.

He did not make it openly, but feel did I do. Already before this last crisis I was trying to find a way to get a trade in Germany. The official ways here expect a traceable life path, which is nowadays increasingly sensitive to scrutiny.

The way he conducted the interaction awoke something in me. He asked questions for which he knew the answers. He nodded in acknowledgment as if he was surprised. He smiled as if it meant only appreciation. It might be strange to anyone who was never there down deep that having ideas was a remarkable thing---but they are.

%\input{separators/sep-line-1.tex}
%\input{separators/sep-ast-1.tex}
%\input{separators/sep-scshape-1.tex}
\input{separators/sep-3-diamond-1.tex}
%\input{separators/sep-quadding-1.tex}
%\input{separators/sep-3-asterisk-1.tex}

\chapter*{Back on feet}

\enquote{It is beautiful---wonderful,} I said.

Mal smiled pleased, said: \enquote{Glad you liked it.}

I retorted, \enquote{But it was a risky move.}

\enquote{Well worth seeing your face now.}

It was a piece of jewelry that I had never seen before---or if I had seen, unconsciously suppressed: a very realistic prosthetic eye, nearly identical to my natural one, mounted into a silver socket, sculpted eyelashes, making a pendant, on a simple silver chain with round links. I wonder how he did it---I do not remember him taking any photos of me, he knows that I do not like being photographed.

I do not know if he intuited what I then realized, but I noticed at that moment that even after all those years of practice I still had some wariness, self-consciousness about my eyes. Wearing it, looking at the mirror, felt like this was what was missing.

Oh, how lucky I am to have him.
