\chapter*{Explanations}\label{explanations}
\addcontentsline{toc}{chapter}{Explanations}

I understand that she needs time. I have been bracing for this moment since I made the decision, nearly two decades ago. I always knew this moment would come. And I never imagined how unprepared I would feel when it finally came.

I feel physical pain in my body, a pain that comes from seeing her suffering, and from knowing that I am the reason of her suffering.

I approach her from behind, she is giving me her back, watching through the window and I know why. I touch her shoulders lightly, just to deliver her a tactile confirmation that I want to be with her. 

I tell her, \enquote{Hey, there is a lot of things that I can explain to you. First, my reasons, of course. But also about the technical side. I would prefer that you get it from me than from some internet source.}

She stays silent for some moments. Then a reply, \enquote{Okay. Just give me some moments.}

And she goes to gather a paper notebook and a pencil. I take my usual seat at our small wooden kitchen table while she scribes vigorously one bullet point after the other. I feel proud of her. 

I look at her and I wonder if the fact that she looks so little like her mother is why I love her so much. The straightness of the hair does not match, the facial structure is different, probably a consequence of repeated rhinitis and sinusitis during childhood, even the height and body build differ. So many things can influence how bodies develop, what to say about minds?

She wakes me up from my daydream, asks, \enquote{So, what is my legal situation? In Germany?}

Straight to the point---that's my girl. I tell her what I always knew and kept up-to-date, \enquote{German law consider all human beings worth of human dignity, independently of how they come into existence. The process by which you came to life is not allowed in Germany, but you had no part in it and cannot be blamed. If at all, I would be the criminal, if it were done here\dots~but it was not, it was in China, and there, it is legal.}

\enquote{So, none of us is going to prison?}

I reassure her, \enquote{No, neither you, nor me. And the genetics clinic is now allowed to share the information with anyone else without your permission.}

She looks genuinely relieved. She asks, \enquote{Are you sure about that?}

I answer, \enquote{I was sure even before I started everything. I tend to think long-term, Ladybug.}

She gives me the first smile since the revelation, since the result.

\enquote{Okay, next question. But before the question: I understand that you needed to wait until I was\dots~old enough to understand the situation. But then the question: why to mention her as my \enquote{mother} when she is actually something different? I do not have a word for it\dots{}}

I reply, \enquote{\emph{Shoresh}---I suggest that we use that. It is Hebrew for \emph{root.} I guess that it is the best description, in several instances.}

She looks down for several moments. When she looks back at me, there is understanding in her eyes. 

She tells me, \enquote{Yes, I have a father, but I have no mother---I have \emph{Shoresh}. I can live with that. I must live with that. But I want to know who she was. Tell me.}

So I do as requested. I do it calmly, because time is not a problem now. Before the revelation, I feared and dreaded this moment, but now that the worst part is over, I want to savor these moments with her. I want to do it the right way.

I brew us a large pot of tea, the one that we use when there are visitors. And I grab a whole package of oat cookies along with a bar of dark chocolate and some dry fruits.

I assemble all things together on the small rustic wooden center table at our living room and call her to join me. I choose a playlist that, in retrospect, seems that was built exactly for this moment. 
