\chapter*{Probing}\label{probing}
\addcontentsline{toc}{chapter}{Probing}

Coming to work instead of canceling was a good idea. Being busy prevents my thoughts of keeping turning on themselves. Full four hours at the bakery, keeping attentive not to mix up orders, was exactly what I needed. Not something to do my whole life, but perfect until studies start. Perfect for now. 

I change my uniform for my personal clothes. My pals Justyna, Markus and Jan wrote they would be in public open-air gym around 14:00. I can only a bit later than 15:00 but it's okay, they knew I had work. I see them from a distance, taking shelter in the shadows of some small trees near the gym gear. They have spread a towel on the grass for some snacks, Markus has his cooler for drinks.

Markus is the newest addition to my pals circle. Justyna is the oldest, I know her since basic school. We kept in contact even after she decided on technical school. She was always the outgoing one, I met most of my other friends through her. I had the feeling for a while that Markus fancied me. I wondered what would be his reaction if he knew the truth. 

I greet them, grab one soda and lie down near Justyna, laying my head on her lap. She goes on talking about some new singer. I do not care for it. I take her hand and just give it a light squeeze. She answers with another, she knows me well. Does not force with words. She knows something is off. 

\bigskip\noindent\textsc{After an eternity on Justyna's lap, I sit up.} I say, I need your opinion. Of all you three. 

They look at me as if a statue suddenly woke up and started talking to them. The faces ask what kind of opinion, I need no voices.

Very well. Imagine that I am not the person you know. Someone different. Other person, like, substituted. Still Nitzanah but some other one. Would you still be my friends?

They look at each other, a questioning look. I try to be specific, I say, as if I were an adopted child. Not really my father's child. Or my mother's.

Justyna is the nearest to me. She tucks my hair behind my left ear, tells me, Nitzele, what is going on? You are not adopted. Your father once told me that you had lots in common with your mother.

That was new for me. Maybe he did, I never noticed. Why would I? Every child expect to have things in common with parents. Sounds strange now. That I never noticed.

I reply, no, it is not like that. Imagine something different. Like being\dots~generated, I guess. Like in-vitro-fertilization.

Jan intervenes. He wants to study biochemistry, knows more theory. He says, IVF is nothing like adoption, if cells of the father and mother are used in the process. Even if not, or if adoption, I do not see why that would be a problem about who you are. You would still be yourself. 

We stay quiet for a while. Justyna has my hand again. I know she is trying to understand, but she never liked abstract problems. Always practical, and me the dreamy one. 

Jan is distracted with his phone, after his technical declaration. So it is Markus who cracks me. He says, I know what she means. 

I look at him, a panicked look. Pleading with him to stop. He gives me a sad smile and looks down. Gathering time, finding a diversion. Jan and Justyna look at him too, waiting for a continuation. 

He raises his head again, meets my gaze. I know he knows. He says, you fear your mother having betrayed your father, right? It is pretty common, I've read. In some lands up to five percent of all kids. I know of a case, a friend of my father. They only discovered because the child had some genetic problem, so they did tests. Boom, the marriage imploded.

I hear his words, but his eyes tell me another story. He figured it out. The obvious relief on my face after listening to his betrayal tale only confirms it to him. 

Jan starts to explain to me that such tests are not complicated. I could gather DNA from everyday utensils, if I wanted to go the illegal way. Poor Jan, trying to be helpful.

Meanwhile Markus to starts to avoid my look. I stop trying to find his.

When we part to go home, each our own way, I hug Justyna, hug Jan. Markus, the last one, avoids it very naturally. No one notices it but me.