\chapter*{Result}\label{result}
\addcontentsline{toc}{chapter}{Result}

I try to behave normally but I feel that she notices that something is not quite alright. I try to divert her attention, I falsely ask, \enquote{Hey, Ladybug, why are you so nervous? Remember, this is more about possible kids than it is about you\dots{}} and I instantly regret it and want to take it back.

She looks at me with an inquiring look and gives me no answer---she is not nervous at all. I am.

I will regret these last moments of innocence forever, because I am tarnishing them. 

\bigskip\noindent\textsc{The news hits like a stone falling on stamped earth.} The physician looks at me with the knowing look that I was expecting. Nitzanah silences at my side the way I expected, for long moments. The physician is friendly enough to give us time. 

I do not dare to look at her. Like the coward that I am, I hide behind the armrests of my chair. Minutes, hours, days go by---the physician is understanding enough to have postponed all his other appointments.

She is clinging to me and I weep. A nurse comes in, the physician orders something. We are both brought to another room. I take the medication the physician ordered---she does it too. It will help, the nurse says. 

\bigskip\noindent\textsc{An eternity goes by.} The clinic's personnel orders a taxi, we are brought home. The driver follows us until the apartment's entrance and makes sure we get inside. A patient's taxi driver.

Now the most dreaded moment: to be alone with her.