\chapter*{Talk}\label{talk}
\addcontentsline{toc}{chapter}{Talk}

He wants to hide but I won't let him. I block the narrow corridor that leads to the apartment's kitchen and rooms. I demand answers, I want them now, but he won't do it now. He says he will explain everything later.

He confirms that he knew it, all along. I spit out the truth, that he never told me, never hinted at anything. He replies that there would never be an ideal moment and my adulthood presented the best opportunity. I feel like I was a puppet being pulled by strings this whole time. I know that parents manage their kids and don't always tell everything, but this is too much.

He asks for time, to rest, to bring \enquote{order to his thoughts.} What about my thoughts, my feelings? I am the victim here, I remind him. I see that it hurts and I feel a jolt of joy but also a sting of sadness. I give him the time he wants.

I hear him call in sick at work. He promises to have the whole following day free for talk.

\bigskip\noindent\textsc{The news hits like a stone falling on stamped earth.} The physician looks at me with the knowing look that I was expecting. Nitzanah silences at my side the way I expected, for long moments. The physician is friendly enough to give us time. 

I do not dare to look at her. Like the coward that I am, I hide behind the armrests of my chair. Minutes, hours, days go by---the physician is understanding enough to have postponed all his other appointments.

She is clinging to me and I weep. A nurse comes in, the physician orders something. We are both brought to another room. I take the medication the physician ordered---she does it too. It will help, the nurse says. 

\bigskip\noindent\textsc{An eternity goes by.} I sleep through the afternoon, she apparently too. One might assume that a genetics clinic has preparedness for stressful revelations of all kind. The clinic's personnel orders a taxi, we are brought home. The driver follows us until the apartment's entrance and makes sure we get inside. A patient's taxi driver.

Now the most dreaded moment: to be alone with her.