\chapter*{Understanding}\label{understanding}
\addcontentsline{toc}{chapter}{Understanding}

He did well. I realize now that he has been preparing for this moment all my life. The revelation via medical examinations might not have been planned, but was an opportunity well used.

The information package was also very helpful. Planned to be explanatory enough. For a layperson. Standing in the park, now, might seem spontaneous, but I am sure he had it planned.

I feel grateful but also hateful. Grateful wins. I decide to talk again. I point to a bench under a tree. 

Correct me if I am wrong.

Right.

My\dots~mind? My mind is my own because brains develop differently.

Right. Remember the comparison with twins, who are undoubtedly different persons. 

So it's like she is my sister, not my mother.

Right. If one of the twin embryos were frozen for years and only later implanted, it would be the same.

Nothing in the information package is as simple as that. Why?

Because people make it more complicated than it is, because of social, psychological, religious aspects. No wonder many countries still prohibit it. So many people still think that it is about making \enquote{copies,} or even worse, \enquote{backups} of oneself. But as someone who knew you both I can assure you: you both have very distinctive personalities.

You never talked much about her. Was it to avoid influencing me?

Not exactly. I did not do it at first because it hurt\dots~and later on because you in my life was all I needed. I did not forget her, but there was no longer a painful void.

I guess that it is enough for now. Not forever, just for now. May I ask again anytime?

Of course! Anytime, anything.

I lean on his shoulder for a while. I can feel his heartbeat. It was faster right after the talk, then got slower. He takes my hand, presses it lightly. I try to quantify how much more he had to invest than usual parents. Personal effort, money, sacrifices in his career. I cannot quantify.

I feel overwhelmed by the thought. My arm thrown over his shoulders bringing him closer tells him that.  